Ideal model selection is impossible

### 2014-10-22 Facticity/Facticity/paper.tex
Mijn versie...

>>>>

\begin{proof}
We first note that 
\begin{equation}
	K(yx) + K(|y|) + c' \geq K(x) \label{line:prelim1}
\end{equation}
for some constant $c$, since we can combine the shortest program to produce $yx$ and the shortest program for the length of $y$ to create a program which produces $yx$ and removes the first $|y|$ bits.

Let $r$ be some string such that 
\begin{equation}
|r| - K^\phi(|r|) - c' > c \quad \text{,} \label{line:prelim2}\\
\end{equation}

with $c$ as given in the statement of the lemma. Define psi as $\psi_{ri}(x) = \phi_{i}(x)$, with $\psi_{j}(x) = \infty$ if $j$ cannot be read as $ri$. Note that this gives us 
\begin{equation}
K^\psi(x) \geq K^\phi(x) + |r| \label{line:prelim3}
\end{equation} 
for all $x$.

We can now state the following:
\begin{align*}
K^\psi(f) &= \min\left\{ K^\psi(j) : \psi_j = f \right\}& \\
       &= \min\left\{ K^\psi(ri) : \psi_{ri} = f \right\}& \\
       &\geq \min\left\{ K^\phi(ri) + |r| : \psi_{ri} = f \right\}& \text{by \ref{line:prelim3}}\\
       &= \min\left\{ K^\phi(ri) : \phi_{i} = f \right\} + |r| & \\
       &\geq \min\left\{ K^\phi(i) - K^\phi(|r|) - c': \phi_{i} = f \right\} + |r| & \text{by \ref{line:prelim1}}\\
       &= \min\left\{ K^\phi(i) : \phi_{i} = f \right\} + |r| - K^\phi(|r|) - c' &\\
       &= \min\left\{ K^\phi(i) : \phi_{i} = f \right\} + |r| - K^\phi(|r|) - c' &\\
       &= K^\phi(f) + |r| - K^\phi(|r|) - c' &  \\
       &\geq K^\phi(f) + c & \text{by \ref{line:prelim2}} \\
\end{align*}
